An assessment of photometric redshift PDF performance in the context of LSST

### 2018-11-28 paper/main.tex
remove old conclusions section

\input{./tex/conclusion}

@@

The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.

@@

In addition to packages cited in the text, analyses performed in this paper used the following software packages: \textsc{Numpy} and \textsc{Scipy} \citep{numpyscipy}, \textsc{Matplotlib} \citep{matplotlib}, \textsc{Seaborn} \citep{seaborn}, \textsc{minFunc} \citep{minfunc}, and {\textsc photUtils} in the LSST simulations package \citep{lsstphotutils}.

>>>>

%\input{./tex/conclusion}

@@

The authors would like to thank their LSST-DESC publication review committee.

{ \red{personal funding sources}}

@@
